#
# r | art
#

```{r}
library(tidyverse)
```

```{r}
golden_ratio <- (1+sqrt(5))/2
golden_angle <- pi*(3-sqrt(5))

gold_titanium = c("#eba584", "#d4a67c", "#c3ad95", "#554e41")
slate = c("#383836")
```

```{r}
linearInterpolate <- function(a, b, t) {
    return((1-t)*a + t*b)
}

dot <- function(a, b) {
    return(a.x*b.x + a.y*b.y)
}

vlength <- function(a) {
    return(dot(a, a))
}
```

```{r}

fade <- function(t) {
    return(t*t*t * (t * (t * 6 - 15) + 10))
}

grad <- function(h, x, y, z) {
    h <- bitwAnd(h, 15)
    u <- ifelse(h<8, x, y)
    v <- ifelse(h<4, y, ifelse(h==12 || h==14, x, z))
    return(ifelse((bitwAnd(h, 1))==0, u, -u) + ifelse((bitwAnd(h, 2))==0, v, -v))
}

disney_noise <- function(x, y, z) {
    n <- 512
    p <- vector(mode="numeric", length=n)

    X <- bitwAnd(floor(x), 255)
    Y <- bitwAnd(floor(y), 255)
    Z <- bitwAnd(floor(z), 255)

    x <- x - floor(x)
    y <- y - floor(y)
    z <- z - floor(z)

    u = fade(x)
    v = fade(y)
    w = fade(z)

    # <<

    permutation <- c(151,160,137,91,90,15,
        131,13,201,95,96,53,194,233,7,225,140,36,103,30,69,142,8,99,37,240,21,10,23,
        190,6,148,247,120,234,75,0,26,197,62,94,252,219,203,117,35,11,32,57,177,33,
        88,237,149,56,87,174,20,125,136,171,168,68,175,74,165,71,134,139,48,27,166,
        77,146,158,231,83,111,229,122,60,211,133,230,220,105,92,41,55,46,245,40,244,
        102,143,54,65,25,63,161,1,216,80,73,209,76,132,187,208,89,18,169,200,196,
        135,130,116,188,159,86,164,100,109,198,173,186,3,64,52,217,226,250,124,123,
        5,202,38,147,118,126,255,82,85,212,207,206,59,227,47,16,58,17,182,189,28,42,
        223,183,170,213,119,248,152,2,44,154,163,70,221,153,101,155,167,43,172,9,
        129,22,39,253,19,98,108,110,79,113,224,232,178,185,112,104,218,246,97,228,
        251,34,242,193,238,210,144,12,191,179,162,241,81,51,145,235,249,14,239,107,
        49,192,214,31,181,199,106,157,184,84,204,176,115,121,50,45,127,4,150,254,
        138,236,205,93,222,114,67,29,24,72,243,141,128,195,78,66,215,61,156,180
    )

    for (i in seq(1, 256, 1)) {
        p[i] = permutation[i]
        p[256+i] = permutation[i]
    }

    # >>

    A <- p[X+1]+Y
    AA <- p[A+1]+Z
    AB <- p[A+2]+Z
    B <- p[X+2]+Y
    BA <- p[B+1]+Z
    BB <- p[B+2]+Z

    result <- linearInterpolate(linearInterpolate(linearInterpolate(grad(p[AA+1], x, y, z),
                                                                    grad(p[BA+1], x-1, y, z),
                                                                    u),
                                                  linearInterpolate(grad(p[AB+1], x, y-1, z),
                                                                    grad(p[BB+1], x-1, y-1, z),
                                                                    u),
                                                  v),
                                linearInterpolate(linearInterpolate(grad(p[AA+2], x, y, z-1),
                                                                    grad(p[BA+2], x-1, y, z-1),
                                                                    u),
                                                  linearInterpolate(grad(p[AB+2], x, y-1, z-1),
                                                                    grad(p[BB+2], x-1, y-1, z-1),
                                                                    u),
                                                  v),
                                w)

    return(result)
}

```

# circle

```{r}
seq(0, 1, .01) %>%
data.frame(a=.) %>%
ggplot(aes(x=a, y=0)) +
geom_point(alpha=.2, color="#000000", size=0) +
coord_polar() +
theme_void()
```

# flower | rose

```{r}
seq(-pi, pi, .01) %>%
data.frame(a=.) %>%
ggplot(aes(x=a, y=2*sin(4*a))) +
geom_point(alpha=.2, color="#000000", size=0) +
coord_polar() +
theme_void()
```

# flower | rose #2

```{r}
seq(-2*pi, 2*pi, .01) %>%
data.frame(a=.) %>%
ggplot(aes(x=a, y=cos(3*a))) +
geom_point(alpha=.2, color="#000000", size=0) +
coord_polar() +
theme_void()
```

# golden flower

```{r}
(seq(0, 100, 1) * golden_angle) %>%
data.frame(a=., x=sin(.), y=cos(.)) %>%
ggplot(aes(x=a*x, y=a*y)) +
geom_point(aes(color=a, size=0), alpha=.1, show.legend=F) +
scale_color_gradientn(colors=gold_titanium) +
theme_void() +
theme(plot.background=element_rect("#f4f4f4")) +
theme(plot.margin=unit(c(4, 4, 4, 4), "cm"))
```

# lisa

```{r}
a <- 1
b <- 1
c <- 1
A <- 10
B <- 10

(seq(-2*pi, 2*pi, .1)) %>%
data.frame(t=.) %>%
ggplot(aes(x=A*sin(a*t+c), y=B*sin(b*t))) +
geom_point(aes(color=t, size=0), alpha=.1, show.legend=F) +
scale_color_gradientn(colors=gold_titanium) +
theme_void() +
theme(plot.background=element_rect("#f4f4f4")) +
theme(plot.margin=unit(c(4, 4, 4, 4), "cm"))
```

# rose

```{r}
n <- 8
d <- 4

angle <- 10*(pi/180)

makeRose <- function(n, d, angle) {
    r <- (seq(0, 8*pi, .04)) %>%
    data.frame(t=.) %>%
    mutate(x=cos(n/d*t)*cos(t), y=cos(n/d*t)*sin(t)) %>%
    mutate(xx=x*cos(angle)-y*sin(angle), yy=x*sin(angle)+y*cos(angle)) %>%
    ggplot(aes(x=xx, y=yy)) +
    geom_point(aes(color=t, size=0), alpha=.1, show.legend=F) +
    scale_color_gradientn(colors=slate) +
    theme_void() +
    theme(plot.background=element_rect("#f4f4f4")) +
    theme(plot.margin=unit(c(4, 4, 4, 4), "cm"))
    return(r)
}

rose <- makeRose(8, 4, 0)
rose
```

# rose animation

```{r}

easeInOutCubic <- function(x) {
    return(ifelse(x < 0.5, 4*x*x*x, 1 - ((-2*x+2)^3) / 2))
}

sequence <- seq(0, 1, 1/60) %>% easeInOutCubic() %>% `*`(2*pi)

imap(sequence, function(angle, i) {
    rose <- makeRose(8, 4, angle)
    fn <- paste(str_pad(i-1, 2, "left", "0"), "png", sep=".")
    ggsave(fn, rose, units="in", width=1800/300, height=1800/300)
})

```

# xy <3

```{r}

# shape (201, 1) -> (40401, 2)

seq(-1, 1, .01) %>%
expand.grid(x=., y=.) %>%
ggplot(aes(x=pi*x-cos(y^2), y=1-sin(x^2))) +
geom_point(alpha=.02, color="#000000", size=0) +
coord_polar() +
theme_void()
```

# xyz

```{r}
seq(-pi, pi, .1) %>%
expand.grid(x=., y=., z=.) %>%
ggplot(aes(x=x+y+z, y=x*y*z)) +
geom_point(alpha=.1, color="#000000", size=0) +
coord_polar() +
theme_void()
```

# xyz #2

```{r}
get_log <- function(filename) {
    if (file.exists(filename)) {
        return(read.csv(filename, sep="\t"))
    }
    return(data.frame(date=NA, seed=NA, x=NA, y=NA))
}
```

```{r}
model <- list(
    x=quote(runif(1,-1,1)*x+runif(1,-1,1)*y^2+runif(1,-1,1)*z^3),
    y=quote(runif(1,-1,1)*x+runif(1,-1,1)*y+runif(1,-1,1)*z)
    )

log <- "log.csv"
sequence <- seq(0, 1, 1)
seeds <- sample(1:1000, length(sequence))
log_df = get_log(log)

seeds_log <- log_df %>%
    dplyr::filter(x == as.character(model["x"])) %>%
    dplyr::filter(y == as.character(model["y"])) %>%
    dplyr::filter(seed %in% seeds) %>%
    dplyr::pull(seed) %>%
    unique(.)

seeds <- seeds[(!(seeds %in% seeds_log))]

result <- map(seeds, function(seed) {
    set.seed(seed)

    a <- seq(-pi, pi, .1) %>%
    expand.grid(x=., y=., z=.) %>%
    mutate(!!!model) %>%
    ggplot(aes(x=x, y=y)) +
    geom_point(alpha=.08, color="#000000", size=0) +
    coord_polar() +
    theme_void()

    t <- format(Sys.time(), format="%F_%H-%M-%S")
    fn <- paste(paste(t, seed, sep="_"), "png", sep=".")

    ggsave(fn, a, units="in", width=1800/300, height=1800/300)

    log_df <- get_log(log)
    new_df <- data.frame(date=t, seed=seed, x=as.character(model["x"]), y=as.character(model["y"]))
    log_df <- bind_rows(log_df, new_df)
    write.table(log_df, log, sep="\t", row.names=F)
})
```

# save

```{r}
t <- format(Sys.time(), format="%F_%H-%M-%S")
fn <- paste(t, "png", sep=".")
ggsave(fn, units="in", width=1800/300, height=1800/300)
```
